The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-28 paper.tex
update

  Note that as we inject the jets within the clumpy disk,\
  we define the ambient gas density by the peak density of\
  the isothermal disk on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.

@@

  The bipolar jets are constantly and bidirectionally ejected from a cylindrical source\
  with diameter and height of 4 pc, leading to the volume $\sim 50 \text{pc}^{3}$,\
  much smaller than that of individual clump by a factor of 83.\
  By intentionally reducing the ratio of the volume of jet source and of clump,\
  we

  We resolve the jet source at the center of the simulation domain,\
  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\

  Source size is much smaller than clump

>>>>

  Note that as we inject the jets at the center of the clumpy disk,\
  we define the ambient gas density by the peak density of\
  the isothermal disk on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.

@@

  The bipolar jets are constantly and bidirectionally ejected from a cylindrical source\
  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{pc}^{3}$ is\
  much smaller than that of individual clump by a factor of 83.\
  By intentionally reducing the volume ratio of the jet source to an individual clump,\
  we can diminish the effect of the randomness of the clumps on the bubbles.

  We resolve the jet source with the highest refinement level 11,\
  bringing the finest spatial resolution up to 0.4 pc.\
